WASP-4\lowercase{b} Arrived Early for the TESS Mission

### 2018-12-12 paper/ms.tex
syntax purging

\author[0000-0002-0514-5538]{L. G. Bouma}
\affiliation{ Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
\author[0000-0002-4265-047X]{J. N. Winn}
\affiliation{ Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
\author[0000-0002-0875-8401]{J.-M. D\'esert}
\affiliation{ API, University of Amsterdam, P.O. Box 94249, 1090 GE
Amsterdam, The Netherlands}
%
\author[0000-0002-3481-9052]{K. G. Stassun}
\affiliation{Vanderbilt University, Department of Physics \& Astronomy,
6301 Stevenson Center Lane, Nashville, TN 37235, USA}
\affiliation{Fisk University, Department of Physics, 1000 17th Avenue
N., Nashville, TN 37208, USA}
%
\author[0000-0002-6939-9211]{T. Daylan}
\affiliation{ Department of Physics and Kavli Institute for Astrophysics
and Space Research, Massachusetts Institute of Technology, Cambridge, MA
02139, USA }
%
\author[0000-0002-7084-0529]{S. Kane}
\affiliation{Department of Earth Sciences, University of California,
Riverside, CA 92521, USA}
% 
%-------------------------------------
% TESS Mission Architects:
% These authors should be listed in this order
% see https://spacebook.mit.edu/pages/viewpage.action?pageId=24543276
%-------------------------------------
%
\author{G. R. Ricker} % grr@space.mit.edu WAITING
\affiliation{ Department of Physics and Kavli Institute for Astrophysics
and Space Research, Massachusetts Institute of Technology, Cambridge, MA
02139, USA }
%
\author[0000-0001-6763-6562]{R. Vanderspek} % roland@space.mit.edu WAITING
\affiliation{ Department of Physics and Kavli Institute for Astrophysics
and Space Research, Massachusetts Institute of Technology, Cambridge, MA
02139, USA }
%
\author[0000-0001-9911-7388]{D. W.~Latham} % dlatham@cfa.harvard.edu WAITING
\affiliation{ Harvard-Smithsonian Center for Astrophysics, 60 Garden
Street, Cambridge, MA 02138, USA }
%
\author{S. Seager} % seager@mit.edu WAITING
\affiliation{ Department of Earth, Atmospheric, and Planetary Sciences,
Massachusetts Institute of Technology, Cambridge, MA 02139, USA }
%
\author[0000-0002-4715-9460]{J. M.~Jenkins} % jon.jenkins@nasa.gov WAITING
\affiliation{ NASA Ames Research Center, Moffett Field, CA 94035, USA }
%
%-------------------------------------
% 3 representatives of each of SPOC, POC, TSO, for a total of 9. 
%These 9 authors should be listed in alphabetical order
%-------------------------------------
% 3 TSO COAUTHORS
%
\author[0000-0002-3321-4924]{Z. Berta-Thompson} % Zachory.BertaThompson@Colorado.EDU WAITING
\affiliation{Department of Astrophysical and Planetary Sciences,
University of Colorado, Boulder, CO 80309, USA}
%
\author[0000-0001-8812-0565]{J. Rodriguez} % rodriguez.jr.joey@gmail.com WAITING
\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden
Street, Cambridge, MA 02138, USA }
%
\author[0000-0001-8020-7121]{K. Col\'on} % knicole.colon@nasa.gov WAITING
\affiliation{NASA Goddard Space Flight Center, Exoplanets and Stellar
Astrophysics Laboratory (Code 667), Greenbelt, MD 20771, USA}
% 3 SPOC COAUTHORS
%
\author[0000-0002-6778-7552]{J. D. Twicken} % Joseph.Twicken@nasa.gov WAITING
\affiliation{ NASA Ames Research Center, Moffett Field, CA 94035, USA }
\affiliation{ SETI Institute, Mountain View, CA 94043, USA}
%
\author{B. Wohler} % bill.wohler@nasa.gov WAITING
\affiliation{ NASA Ames Research Center, Moffett Field, CA 94035, USA }
\affiliation{ SETI Institute, Mountain View, CA 94043, USA}
%
\author[0000-0003-1963-9616]{D. A. Caldwell} % douglas.Caldwell@nasa.gov % WAITING
\affiliation{ NASA Ames Research Center, Moffett Field, CA 94035, USA }
\affiliation{ SETI Institute, Mountain View, CA 94043, USA}
%
%\\ \textcolor{red}{3 POC coauthors:}
\author{POC1}
\author{POC2}
\author{POC3}

\begin{abstract}
  %TODO: final numbers
  By combining data from the Transiting Exoplanet Survey Satellite
  (TESS) with data from previous studies, we show that the transit
  times of WASP-4b are incompatible with a constant orbital period.
  The transits observed by TESS occurred $77.8 \pm 10.8$~seconds
  earlier than one would expect, based on the previous data.  The
  orbital period appears to be shrinking by $\dot{P}=-12.1 \pm 1.2$
  milliseconds per year.   A simple clock offset is unlikely, because
  TESS observations of other hot Jupiters (WASP-6b, 18b, and 46b) are
  compatible with a constant period and rule out a 77.8-second offset
  at the 6.3$\sigma$ level.  The timing variations seem to be
  astrophysical, and could be caused by apsidal precession, or perhaps
  by tidal decay.  The latter seems implausible on theoretical
  grounds, as it would require a stellar quality factor $Q_\star'
  \approx 3\times10^4$.  Apsidal precession would imply an
  eccentricity $e\approx1.6\times 10^{-3}$, and the possibility of
  measuring the planet's Love number.  A Doppler shift from WASP-4's
  acceleration towards us could account for at most one quarter of the
  observed period change (at $2\sigma$).  Further observations will
  help confirm the reality of the timing variation, and eventually
  determine its cause.
\end{abstract}

@@

The second process that long-term timing studies should reveal is
apsidal precession, {\it i.e.}, rotation of the orbital ellipse within
the orbital plane. Apsidal precession has been observed extensively in
eclipsing binaries \citep[{\it e.g.},][]{
  schwarzschild_structure_1958,torres_accurate_2010,borkovits_eclipse_2015},
and has been detected in a handful of exoplanet systems, including
circumbinary planets (Kepler-413 \citealt{kostov_kepler-413b_2014};
Kepler-453 \citealt{welsh_kepler_2015}, planets orbiting rapidly
rotating stars (Kepler-13
\citealt{szabo_spin-orbit_2012,szabo_mapping_2014,masuda_spin-orbit_2015};
PTFO 8-8695 \citealt{barnes_measurement_2013}), and systems with
multiple interacting giant planets (Kepler-108
\citealt{mills_kepler-108_2017}; Kepler-693
\citealt{masuda_eccentric_2017}).  Apsidal precession is not regularly
observed in hot Jupiter systems, perhaps in part because their orbits
are nearly circular.  However, there are many mechanisms that
could pump hot Jupiter orbits away from circularity (see
\S~\ref{sec:apsidal_precession}, and
\citealt{bailey_understanding_2019}), which would then lead to
observable timing variations.  For hot Jupiters, the apsidal
precession is usually dominated by the quadrupolar distortion of the
planet by the star's tidal force \citep{ragozzine_probing_2009}.  The
observed precession rate in a hot Jupiter system could thus be used to
compute the planet's Love number, giving a third parameter along with
the mass and radius with which to describe the planet's interior
structure \citep[{\it e.g.},][who performed a similar procedure for
HAT-P-13b]{batygin_determination_2009}.  Measuring small
eccentricities and understanding their origin might also help us
understand the dynamical histories and inflated radii of hot Jupiters.
\citep[{\it
e.g.},][respectively]{dawson_origins_2018,ibgui_tidal_2010}

@@

The TESS spacecraft recorded images of WASP-4 in an $11\times11$ pixel
array every 2 minutes.   After being downlinked through the Deep Space
Network, the data were processed through the Science Processing
Operations Center (SPOC) pipeline at NASA
Ames~\citep{jenkins_tess_2016}.  One important step in this processing
was converting from spacecraft time to barycentric time.  SPOC then
reports timestamps in ``BTJD'', where ${\rm BTJD} = {\rm BJD} -
2457000$, BJD is the barycentric julian date, and all times are in the
TDB reference (see \citealt{urban_explanatory_2012} for explanations
of time systems).  The lightcurves were then vetted and released by
the MIT TESS Science Office to the Mikulski Archive for Space
Telescopes~\citep{ricker_tess_alerts_2018}.

We begin our analysis with the Presearch Data Conditioning (PDC) light
curves from MAST.  The steps used to find an optimal aperture (for
WASP-4, a $3\times 3$ pixel array) and the PDC-MAP algorithm are
described by \citet{smith_kepler_apertures_2017} and
\citet{smith_kepler_PDC_2017} respectively.

We then processed the lightcurve as follows.  First, we removed all
points with non-zero quality flags.  This removes data contaminated by
coarse spacecraft pointing, cosmic rays, and other annoyances
\citep{tess_data_product_description_2018}.  We then filtered out
known bad observing windows.  The data closest to spacecraft perigee
typically show ramp-like systematics, so we clipped out the first and
last hour of both orbits.  Next, we focused on the momentum dumps. As
described in the data release
notes\footnote{\url{archive.stsci.edu/hlsps/tess-data-alerts/hlsp_tess-data-alerts_tess_phot_s01_tess_v1_release-notes.pdf}},
during the first two TESS sectors, every 2.5~days the spacecraft's
reaction wheels were reset to maintain pointing stability.  These
events were assigned quality flags corresponding to ``Reaction Wheel
Desaturation Event'' and ``Manual Exclude''.  For WASP-4, these flags
were simultaneously set for 54 distinct cadences, and there were 10
momentum dumps, averaging about 10 minutes of flagged data per dump.
Simply out of caution, we clipped out an additional 10 minutes before
and after every momentum dump.  Before applying any filters, we had
19737 data points. After applying all the filters, we were left with
18165 measurements, or 92\% of the original data.

After ``cleaning'' the data, we normalized the flux measurements by
dividing out the median flux.  We then converted the timestamps from
BTJD to BJD by adding the appropriate 2457000 day offset
\citep{tess_data_product_description_2018}.  Many of these and
subsequent processing steps were performed using
\texttt{astrobase}~\citep{bhatti_astrobase_2018} We opted not to
``flatten'' the lightcurves at this stage, as is often done with {\it
e.g.}, a spline or gaussian process regression.  Such procedures are
asymmetric about the transit minimum and can skew the transit time
measurement without being captured by the measurement uncertainties.

@@

\begin{figure}[t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.48\textwidth]{f2.pdf}
    \end{center}
    \vspace{-0.6cm}
    \caption{
      %TODO: final number
        {\bf TESS saw WASP-4b transit earlier than expected.}
        Points are the
        differences between observed transit times and the
        pre-TESS ephemeris, plotted against
        transit number.
        Blue curves are the
        $\pm 1\sigma$ credible interval around the constant-period
        prediction.
        {\it Top:} The full timing dataset spans 10 years.
                Less precise points are more transparent.
        {\it Bottom:}
        The binned TESS observation (red point) arrived
        $77.8 \pm 10.8\ {\rm seconds}$ before it was expected.
        \label{fig:arrived_early}
    }
\end{figure}

Using the cleaned PDC lightcurve, we ran Box Least Squares (BLS) to
determine the orbital period, and to estimate the transit duration and
a reference epoch \citep{kovacs_box-fitting_2002}.  From these
parameters, we isolated each transit to within $\pm$4 transit
durations of its midtime.  We then fit the phase-folded transit, using
the analytic formulae calculated by \citet{mandel_analytic_2002} and
implemented by \citet{kreidberg_batman_2015}.  Specifically, we fit
for a reference epoch, the planet to star radius ratio $R_{\rm
p}/R_\star$, the semi-major axis to stellar radius ratio $a/R_\star$,
the inclination $i$, two quadratic limb-darkening coefficients
$(u_{\rm linear}, u_{\rm quad})$, and the orbital period $P$.  We set
the eccentricity to zero.

@@

To measure mid-transit times, we then focused on each individual
transit window.  We fit for a model transit, plus a local linear
trend.  We allowed four free parameters per transit: the time of
mid-transit $t_{\rm tra}$, the planet-to-star radius ratio $R_{\rm
p}/R_\star$, and the slope and intercept of the line.  We fixed the
remaining parameters~--~$a/R_\star$, $i$, $P$, and the limb-darkening
coefficients~--~to the best-fit values from the global fit.

% During this process, we used the \texttt{corner} software to check
% that our posteriors were being well-sampled~\citep{corner_2016}.
After completing an initial fit for each transit, we set the
photometric error bars to be equal to the standard deviation of the
out-of-transit points of the residual lightcurve.  We then reperformed
the fitting procedure, using the empirically determined photometric
errors.

@@

Figure~\ref{fig:lightcurves} shows the light curves, best-fit models,
and residuals.  Table~2 reports the mid-transit times and their
uncertainties.
Binning the residuals to 1-hour windows and taking the median absolute
deviation, the lightcurves have an RMS of $586\,{\rm ppm}\,{\rm
hr}^{1/2}$.  The predicted\footnote{\url{github.com/lgbouma/tnm}}
photon-counting noise is $410\,{\rm ppm}\,{\rm hr}^{1/2}$.  At
$T\approx11.8$, with a 9-pixel aperture read noise is expected to
contribute an additional $202\,{\rm ppm}\,{\rm hr}^{1/2}$ in
quadrature.  The predicted zodiacal background contribution is
$673\,{\rm ppm}\,{\rm hr}^{1/2}$, based on the
\citet{winn_photonflux_2013} model, which \citet{Sullivan_2015} used
in planet detection simulations.  This zodiacal noise prediction seems
to have been an overestimate, given the observed RMS of WASP-4.  A
more detailed assessment of TESS's photometric performance is beyond
the scope of this work.

@@

\startdata
%FIXME with new method
%TODO numbers with updated method
{\it Transit/RV parameters:} & & & \\
  $R_{\rm p}/R_\star$                        & $0.1538$               & $\pm 0.0013$                & A \\
  $i$~[deg]                                  & $88.52$                & $+0.39$, $-0.26$            & A \\
  $a/R_\star$                                & $5.463$                & $+0.025$, $-0.020$          & A \\
  $u_{\rm linear}$                           & $0.XXX$                & $+0.XXX$, $-0.XXX$          & A \\
  $u_{\rm quad}$                             & $0.XXX$                & $+0.XXX$, $-0.XXX$          & A \\
  $K$~[m~s$^{-1}$]                           & $241.1$                & $+2.8$, $-3.1$              & B \\
{\it Stellar parameters:} & & & \\
  $T_{\rm eff}$~[K]                          & $5400$                 & $\pm 90$                    & C \\
  $\log g_\star$~[cgs]                       & $4.47$                 & $\pm 0.11$                  & C \\
  $[{\rm Fe/H}]$                             & $-0.07$                & $\pm 0.19$                  & C \\
  $F_{\rm bol}$~[erg~cm$^{-2}$~s$^{-1}$]     & $2.802\times10^{-10}$  & $\pm 0.076\times10^{-10}$   & D \\
  $\pi$~[mas]                                & $3.7145$               & $0.0517$                    & F \\
  $R_\star$~[R$_{\odot}$]                    & $0.893$                & $\pm 0.034$                 & E \\
  $\rho_\star$~[g~cm$^{-3}$]                 & $1.722$                & $+0.024$, $-0.019$          & E \\
  $M_\star$~[M$_{\odot}$]                    & $0.870$                & $+0.085$, $-0.077$          & E \\
  $T$ magnitude                              & $11.778$               & $\pm 0.018$                 & G \\
{\it Planetary parameters:} & & & \\
  $a$~[AU]                                   & $0.0227$               & $\pm 0.0007$                & E \\
  $M_p$~[M$_{\rm Jup}$]                      & $1.192$                & $+0.091$, $-0.086$          & E \\
  $R_p$~[R$_{\rm Jup}$]                      & $1.337$                & $\pm 0.048$                 & E \\
\enddata

@@

\citet{doyle_accurate_2013} found accurate spectroscopic parameters
for WASP-4 using high S/N HARPS spectra.  Using their (T$_{\rm eff}$,
$\log g$, $[{\rm Fe/H}]$) and the available {\it Gaia} parallaxes, we
compute the remaining system parameters empirically.

We compute the bolometric flux using broadband magnitudes from
available all-sky catalogs, as follows: $G$ from {\it Gaia\/} DR2,
$B_T V_T$ from {\it Tycho-2}, $BVgri$ from {\it APASS}, $JHK_S$ from {\it
2MASS}, and the {\it WISE}~1--4 passbands, thus spanning the
wavelength range 0.4--22~$\mu$m.  Combining the implied angular radius
with the {\it Gaia} DR2 parallax, and adjusting for the parallax
offset \citep{stassun_evidence_2018}, we obtain the stellar radius.
For the stellar mass, we started with the $a/R_\star$ value found by
\citet{hoyer_tramos_2013} from 26 ground-based transits.  The implied
semi-major axis and stellar density follow \citep{seager_unique_2003}.
Combining the density and radius gives the stellar mass.  We get the
planet radius using our measured $R_{\rm p}/R_\star$.  Finally, for
the planet mass we use the observed RV semi-amplitude and inclination
angle from the transit
\citep{triaud_spin-orbit_2010,hoyer_tramos_2013}.

>>>>

\author[0000-0002-0514-5538]{L. G. Bouma}
\affiliation{ Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
\author[0000-0002-4265-047X]{J. N. Winn}
\affiliation{ Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
\author[0000-0002-0875-8401]{J.-M. D\'esert}
\affiliation{ API, University of Amsterdam, P.O. Box 94249, 1090 GE
Amsterdam, The Netherlands}
%
\author[0000-0002-3481-9052]{K. G. Stassun}
\affiliation{Vanderbilt University, Department of Physics \& Astronomy,
6301 Stevenson Center Lane, Nashville, TN 37235, USA}
\affiliation{Fisk University, Department of Physics, 1000 17th Avenue
N., Nashville, TN 37208, USA}
%
\author[0000-0002-6939-9211]{T. Daylan}
\affiliation{ Department of Physics and Kavli Institute for Astrophysics
and Space Research, Massachusetts Institute of Technology, Cambridge, MA
02139, USA }
%
\author[0000-0002-5720-4827]{M. Hill}
\affiliation{Department of Earth Sciences, University of California,
Riverside, CA 92521, USA}
%
\author[0000-0002-7084-0529]{S. Kane}
\affiliation{Department of Earth Sciences, University of California,
Riverside, CA 92521, USA}
% 
%-------------------------------------
% TESS Mission Architects:
% These authors should be listed in this order
% see https://spacebook.mit.edu/pages/viewpage.action?pageId=24543276
%-------------------------------------
%
\author{G. R. Ricker} % grr@space.mit.edu WAITING
\affiliation{ Department of Physics and Kavli Institute for Astrophysics
and Space Research, Massachusetts Institute of Technology, Cambridge, MA
02139, USA }
%
\author[0000-0001-6763-6562]{R. Vanderspek} % roland@space.mit.edu WAITING
\affiliation{ Department of Physics and Kavli Institute for Astrophysics
and Space Research, Massachusetts Institute of Technology, Cambridge, MA
02139, USA }
%
\author[0000-0001-9911-7388]{D. W.~Latham} % dlatham@cfa.harvard.edu WAITING
\affiliation{ Harvard-Smithsonian Center for Astrophysics, 60 Garden
Street, Cambridge, MA 02138, USA }
%
\author{S. Seager} % seager@mit.edu WAITING
\affiliation{ Department of Earth, Atmospheric, and Planetary Sciences,
Massachusetts Institute of Technology, Cambridge, MA 02139, USA }
%
\author[0000-0002-4715-9460]{J. M.~Jenkins} % jon.jenkins@nasa.gov WAITING
\affiliation{ NASA Ames Research Center, Moffett Field, CA 94035, USA }
%
%-------------------------------------
% 3 representatives of each of SPOC, POC, TSO, for a total of 9. 
%These 9 authors should be listed in alphabetical order
%-------------------------------------
% 3 TSO COAUTHORS
% 3 SPOC COAUTHORS
% 3 POC COAUTHORS
%
\author[0000-0002-3321-4924]{Z. Berta-Thompson} % Zachory.BertaThompson@Colorado.EDU WAITING
\affiliation{Department of Astrophysical and Planetary Sciences,
University of Colorado, Boulder, CO 80309, USA}
%
\author[0000-0003-1963-9616]{D. A. Caldwell} % douglas.Caldwell@nasa.gov % WAITING
\affiliation{ NASA Ames Research Center, Moffett Field, CA 94035, USA }
\affiliation{ SETI Institute, Mountain View, CA 94043, USA}
%
\author[0000-0001-8020-7121]{K. Col\'on} % knicole.colon@nasa.gov WAITING
\affiliation{NASA Goddard Space Flight Center, Exoplanets and Stellar
Astrophysics Laboratory (Code 667), Greenbelt, MD 20771, USA}
%
\author{M. Fausnaugh} % faus@mit.edu WAITING
\affiliation{ Department of Physics and Kavli Institute for Astrophysics
and Space Research, Massachusetts Institute of Technology, Cambridge, MA
02139, USA }
%
\author[0000-0002-5322-2315]{A. Glidden} % aglidden@mit.edu WAITING
\affiliation{ Department of Physics and Kavli Institute for Astrophysics
and Space Research, Massachusetts Institute of Technology, Cambridge, MA
02139, USA }
%
\author{N. Guerrero} % nmg@mit.edu WAITING
\affiliation{ Department of Physics and Kavli Institute for Astrophysics
and Space Research, Massachusetts Institute of Technology, Cambridge, MA
02139, USA }
%
\author[0000-0001-8812-0565]{J. Rodriguez} % rodriguez.jr.joey@gmail.com WAITING
\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden
Street, Cambridge, MA 02138, USA }
%
\author[0000-0002-6778-7552]{J. D. Twicken} % Joseph.Twicken@nasa.gov WAITING
\affiliation{ NASA Ames Research Center, Moffett Field, CA 94035, USA }
\affiliation{ SETI Institute, Mountain View, CA 94043, USA}
%
\author{B. Wohler} % bill.wohler@nasa.gov WAITING
\affiliation{ NASA Ames Research Center, Moffett Field, CA 94035, USA }
\affiliation{ SETI Institute, Mountain View, CA 94043, USA}
%

\begin{abstract}
  %TODO: final numbers
  By combining data from the Transiting Exoplanet Survey Satellite
  (TESS) with data from previous studies, we show that the transit
  times of WASP-4b are incompatible with a constant orbital period.
  The transits observed by TESS occurred $77.8 \pm 10.8$~seconds
  earlier than one would expect, based on the previous data.  The
  orbital period appears to be shrinking by $\dot{P}=-12.1 \pm 1.2$
  milliseconds per year.   A simple clock offset is unlikely, because
  TESS observations of other hot Jupiters (WASP-6b, 18b, and 46b) are
  compatible with a constant period and rule out a 77.8-second offset
  at the 6.3$\sigma$ level.  The timing variations seem to be
  astrophysical, and could be caused by apsidal precession, or perhaps
  by tidal decay.  The latter seems implausible on theoretical
  grounds, as it would require a stellar quality factor $Q_\star'
  \approx 3\times10^4$.  Apsidal precession would imply an
  eccentricity $e\approx1.6\times 10^{-3}$, and the possibility of
  measuring the planet's Love number.  A Doppler shift from WASP-4's
  acceleration towards us could account for at most one quarter of the
  observed period change (at $2\sigma$).  Further observations are
  needed to confirm and understand the timing variation.
\end{abstract}

@@

The second process that long-term timing studies should reveal is
apsidal precession, {\it i.e.}, rotation of the orbital ellipse within
the orbital plane. Apsidal precession has been observed extensively in
eclipsing binaries \citep[{\it e.g.},][]{
  schwarzschild_structure_1958,torres_accurate_2010,borkovits_eclipse_2015}
and has been detected in a handful of exoplanet systems, including
circumbinary planets (Kepler-413 \citealt{kostov_kepler-413b_2014};
Kepler-453 \citealt{welsh_kepler_2015}, planets orbiting rapidly
rotating stars (Kepler-13
\citealt{szabo_spin-orbit_2012,szabo_mapping_2014},~\citealt{masuda_spin-orbit_2015};
PTFO 8-8695 \citealt{barnes_measurement_2013}), and systems with
multiple interacting giant planets (Kepler-108
\citealt{mills_kepler-108_2017}; Kepler-693
\citealt{masuda_eccentric_2017}).  Apsidal precession is not regularly
observed in hot Jupiter systems, perhaps in part because their orbits
are nearly circular.  However, there are many mechanisms that
could pump hot Jupiter orbits away from circularity (see
\S~\ref{sec:apsidal_precession}, and
\citealt{bailey_understanding_2019}), which would then lead to
observable timing variations.  For hot Jupiters, the apsidal
precession is usually dominated by the quadrupolar distortion of the
planet by the star's tidal force \citep{ragozzine_probing_2009}.  The
observed precession rate in a hot Jupiter system could thus be used to
compute the planet's Love number, giving a third parameter along with
the mass and radius with which to describe the planet's interior
structure \citep[{\it e.g.},][who performed a similar procedure for
HAT-P-13b]{batygin_determination_2009}.  Measuring small
eccentricities and understanding their origin might also help us
understand the dynamical histories and inflated radii of hot Jupiters.
\citep[{\it
e.g.},][respectively]{dawson_origins_2018,ibgui_tidal_2010}

@@

The TESS spacecraft recorded images of WASP-4 in an $11\times11$ pixel
array every 2 minutes.   The data were downlinked via the Deep Space
Network, and the Payload Operations Center then converted the
timestamps from the spacecraft clock to TESS Julian Day in the {\it
Temps Dynamique Barycentrique} (TDB) reference.  The data were then
processed through the Science Processing Operations Center (SPOC)
pipeline at NASA Ames~\citep{jenkins_tess_2016}.  SPOC used the known
spacecraft trajectory to compute the barycentric time corrections on a
target by target basis, and reported timestamps in ``BTJD'', where
${\rm BTJD} = {\rm BJD} - 2457000$, BJD is the barycentric julian
date, and all times are in the TDB reference (see
\citealt{urban_explanatory_2012} for explanations of time systems).
The lightcurves were then vetted and released by the MIT TESS Science
Office to the Mikulski Archive for Space
Telescopes~\citep{ricker_tess_alerts_2018}.

We began our analysis with the Presearch Data Conditioning (PDC) light
curves from MAST.  The steps used to find an optimal aperture (for
WASP-4, a $3\times 3$ pixel array) and the PDC-MAP algorithm are
described by \citet{smith_kepler_apertures_2017} and
\citet{smith_kepler_PDC_2017} respectively.

We processed the lightcurve as follows.  First, we removed all
points with non-zero quality flags.  This removed data contaminated by
coarse spacecraft pointing, cosmic rays, and other annoyances
\citep{tess_data_product_description_2018}.  We then filtered out
known bad observing windows.  The data closest to spacecraft perigee
typically show ramp-like systematics, so we clipped out the first and
last hour of both orbits.  Next, we focused on the momentum dumps. As
described in the data release
notes\footnote{\url{archive.stsci.edu/hlsps/tess-data-alerts/hlsp_tess-data-alerts_tess_phot_s01_tess_v1_release-notes.pdf}},
during the first two TESS sectors, every 2.5~days the spacecraft's
reaction wheels were reset to maintain pointing stability.  These
events were assigned quality flags corresponding to ``Reaction Wheel
Desaturation Event'' and ``Manual Exclude''.  For WASP-4, these flags
were simultaneously set for 54 distinct cadences, and there were 10
momentum dumps, averaging about 10 minutes of flagged data per dump.
Simply out of caution, we clipped out an additional 10 minutes before
and after every momentum dump.  Before applying any filters, we had
19737 data points. After applying all the filters, we were left with
18165 measurements, or 92\% of the original data.

After ``cleaning'' the data, we normalized the flux measurements by
dividing out the median flux.  We converted the timestamps from BTJD
to BJD by adding the appropriate 2457000 day offset
\citep{tess_data_product_description_2018}.  Many of these and
subsequent processing steps were performed using
\texttt{astrobase}~\citep{bhatti_astrobase_2018} We opted not to
``flatten'' the lightcurves at this stage, as is often done with {\it
e.g.}, a spline or gaussian process regression.  Such procedures are
asymmetric about the transit minimum and can skew the transit time
measurement without being captured by the measurement uncertainties.

@@

\begin{figure}[t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.48\textwidth]{f2.pdf}
    \end{center}
    \vspace{-0.6cm}
    \caption{
      %TODO: final number
        {\bf TESS saw WASP-4b transit earlier than expected.}
        Both plots show observed transit times minus the pre-TESS
        ephemeris as a function of transit number.  Blue curves are
        the $\pm 1\sigma$ credible interval around the constant-period
        prediction.  {\it Top:} The full timing dataset spans 10
        years.  Less precise points are more transparent.  {\it
        Bottom:} The binned TESS observation (red point) arrived $77.8
        \pm 10.8\ {\rm seconds}$ before it was expected.
        \label{fig:arrived_early}
    }
\end{figure}

Using the cleaned PDC lightcurve, we ran Box Least Squares (BLS) to
estimate the orbital period, transit duration and a reference epoch
\citep{kovacs_box-fitting_2002}.  From these parameters, we isolated
each transit to within $\pm$4 transit durations of its midtime.  We
then fit the phase-folded transit, using the analytic formulae
calculated by \citet{mandel_analytic_2002} and implemented by
\citet{kreidberg_batman_2015}.  Specifically, we fit for a reference
epoch, the planet to star radius ratio $R_{\rm p}/R_\star$, the
semi-major axis to stellar radius ratio $a/R_\star$, the inclination
$i$, two quadratic limb-darkening coefficients $(u_{\rm linear},
u_{\rm quad})$, and the orbital period $P$.  We set the eccentricity
to zero.

@@

To measure mid-transit times, we then focused on each individual
transit window.  We fit for a model transit, plus a local linear
trend.  We allowed four free parameters per transit: the time of
mid-transit $t_{\rm tra}$, the planet-to-star radius ratio, and the
slope and intercept of the line.  We fixed the remaining
parameters~---~$a/R_\star$, $i$, $P$, and the limb-darkening
coefficients~---~to the best-fit values determined from the
phase-folded TESS lightcurve.

After completing an initial fit for each transit, we set the
photometric error bars to equal the standard deviation of the
out-of-transit points of the residual lightcurve.  We then reperformed
the fitting procedure, using the empirically determined photometric
errors.

@@

% TODO: final numbers
Figure~\ref{fig:lightcurves} shows the lightcurves, best-fit models,
and residuals.  Table~2 reports the mid-transit times and their
uncertainties.
Binning the residuals to 1-hour windows and taking the median absolute
deviation, the lightcurves have an RMS of $586\,{\rm ppm}\,{\rm
hr}^{1/2}$.  The predicted\footnote{\url{github.com/lgbouma/tnm}}
photon-counting noise is $410\,{\rm ppm}\,{\rm hr}^{1/2}$.  At
$T\approx11.8$, with a 9-pixel aperture read noise is expected to
contribute an additional $202\,{\rm ppm}\,{\rm hr}^{1/2}$ in
quadrature.  The predicted zodiacal background contribution is
$673\,{\rm ppm}\,{\rm hr}^{1/2}$, based on the
\citet{winn_photonflux_2013} model, which \citet{Sullivan_2015} used
in planet detection simulations.  This zodiacal noise prediction seems
to have been an overestimate, given the observed RMS of WASP-4.  A
broader assessment of TESS's photometric performance is beyond
the scope of this work.

@@

\startdata
%TODO numbers with updated method
{\it Transit/RV parameters:} & & & \\
  $R_{\rm p}/R_\star$                        & $0.XXXX$               & $\pm 0.0013$                & A \\
  $i$~[deg]                                  & $XX.XX$                & $+0.39$, $-0.26$            & A \\
  $a/R_\star$                                & $5.XXX$                & $+0.025$, $-0.020$          & A \\
  $u_{\rm linear}$                           & $0.XXX$                & $+0.XXX$, $-0.XXX$          & A \\
  $u_{\rm quad}$                             & $0.XXX$                & $+0.XXX$, $-0.XXX$          & A \\
  $K$~[m~s$^{-1}$]                           & $241.1$                & $+2.8$, $-3.1$              & B \\
{\it Stellar parameters:} & & & \\
  $T_{\rm eff}$~[K]                          & $5400$                 & $\pm 90$                    & C \\
  $\log g_\star$~[cgs]                       & $4.47$                 & $\pm 0.11$                  & C \\
  $[{\rm Fe/H}]$                             & $-0.07$                & $\pm 0.19$                  & C \\
  $F_{\rm bol}$~[erg~cm$^{-2}$~s$^{-1}$]     & $2.802\times10^{-10}$  & $\pm 0.076\times10^{-10}$   & D \\
  $\pi$~[mas]                                & $3.7145$               & $0.0517$                    & F \\
  $R_\star$~[R$_{\odot}$]                    & $0.893$                & $\pm 0.034$                 & E \\
  $\rho_\star$~[g~cm$^{-3}$]                 & $1.722$                & $+0.024$, $-0.019$          & E \\
  $M_\star$~[M$_{\odot}$]                    & $0.870$                & $+0.085$, $-0.077$          & E \\
  $T$ magnitude                              & $11.778$               & $\pm 0.018$                 & G \\
{\it Planetary parameters:} & & & \\
  $a$~[AU]                                   & $0.0227$               & $\pm 0.0007$                & E \\
  $M_p$~[M$_{\rm Jup}$]                      & $1.192$                & $+0.091$, $-0.086$          & E \\
  $R_p$~[R$_{\rm Jup}$]                      & $1.337$                & $\pm 0.048$                 & E \\
\enddata

@@

\citet{doyle_accurate_2013} found accurate spectroscopic parameters
for WASP-4 using high S/N HARPS spectra.  Using their (T$_{\rm eff}$,
$\log g$, $[{\rm Fe/H}]$) and the available {\it Gaia} parallaxes, we
calculate the remaining system parameters empirically.

We compute the bolometric flux using broadband magnitudes from
available all-sky catalogs, as follows: $G$ from {\it Gaia\/} DR2,
$B_T V_T$ from {\it Tycho-2}, $BVgri$ from {\it APASS}, $JHK_S$ from {\it
2MASS}, and the {\it WISE}~1--4 passbands, thus spanning the
wavelength range 0.4--22~$\mu$m.  Combining the implied angular radius
with the {\it Gaia} DR2 parallax, and adjusting for the parallax
offset \citep{stassun_evidence_2018}, we obtain the stellar radius.
For the stellar mass, we started with the $a/R_\star$ value found from
the phase-folded TESS lightcurve.  The implied stellar density follows
\citep{seager_unique_2003}, and using the stellar radius we obtain the
semi-major axis and stellar mass.  We get the planet radius using our
measured $R_{\rm p}/R_\star$.  Finally, for the planet mass we use the
observed RV semi-amplitude and inclination angle from the transit
\citep{triaud_spin-orbit_2010}.

We list the resulting parameters in Table~3, and adopt them for the
remaining analysis.  Our parameters broadly agree with those of
previous authors
\citep{wilson_wasp-4b_2008,gillon_discovery_2009,winn_transit_2009,southworth_homogeneous_2011,petrucci_no_2013}.
Comparing our empirical result with the Yonsei-Yale evolutionary track
predicted by the spectroscopic parameters, we see that WASP-4 has an
age $\approx 7\,{\rm Gyr}$, and is securely in the main-sequence stage
of evolution.
